tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-09-16 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Add three peak stat comparison to main heatmap

```{r mero_asex_malegam}
mero_asex_malegam_stats_df <- filter(berghei_comparison_stats_df,
                                     contrast %in% c('Asex.Mixed-Liv.Meroz',
                                                     'Gam.Male-Asex.Mixed',
                                                     'Gam.Male-Liv.Meroz'))

order_path.names <- ordering(sort(unique(mero_asex_malegam_stats_df$pathway.name)), 
                             order_vector = c('pir', 
                                              'L', 'L[[:digit:]]', 
                                              'S', 'S[[:digit:]]'))

mero_asex_malegam_stats_df <- mero_asex_malegam_stats_df[order(match(mero_asex_malegam_stats_df$pathway.name,order_path.names)),]

max_logfold <- ceiling(max(max(mero_asex_malegam_stats_df$log.fold.change), 
                           abs(min(mero_asex_malegam_stats_df$log.fold.change))))

mero_asex_malegam_stats_df_cast <- dcast(mero_asex_malegam_stats_df,
      contrast ~ pathway.name,
      value.var = 'log.fold.change') %>% 
  column_to_rownames(var = 'contrast')

mero_asex_malegam_stats_df_cast <- mero_asex_malegam_stats_df_cast[,order_path.names]

Heatmap(mero_asex_malegam_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          fdr_val <- mero_asex_malegam_stats_df[
            mero_asex_malegam_stats_df$contrast == rownames(mero_asex_malegam_stats_df_cast[i,]),
          ]$FDR[j]
          if(fdr_val<= 0.1){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold')
            )
          }
        })

@@

comparisons <- c(
  unlist(
    lapply(seq_along(ordered_stages),
           function(i){ if(i < length(ordered_stages)){ paste0(ordered_stages[i],'-',ordered_stages[i+1]) } }
    )
  ),
  'Asex.Schiz-Gam.Male',
  'Ook-Sporoz'
)

>>>>

@@

comparisons <- c(
  unlist(
    lapply(seq_along(ordered_stages),
           function(i){ if(i < length(ordered_stages)){ paste0(ordered_stages[i],'-',ordered_stages[i+1]) } }
    )
  ),
  'Asex.Schiz-Gam.Male',
  'Ook-Sporoz',
  'Gam.Male-Asex.Mixed',
  'Gam.Male-Liv.Meroz'
)
